Bias in Allocation of ABM Agents

### 2015-08-30 Rmd/agent-allocation-bias.Rmd
Main paper: Half of results done, bullet points on rest through Discussion (but not yet organized).  Updated cropland bias, carbon bias, yield bias, agent-bias, as worked through results. Earlier results reconfirmed.

cexs <- seq(1, 2, 1 / 3)
pdf(full_path(p_fig, "agent-bias.pdf"), height = 3.5, width = 7)
cx <- c(0.7, 0.8, 0.6)
# png(full_path(p_fig, "agent-bias.png"), height = 350, width = 700)
par(mfrow = c(1, 2), mar = c(3, 2.5, 3, 1), mgp = c(1.5, 0.25, 0), tcl = -0.2, 
    oma = c(0, 0, 0, 4))
scols <- c("red", "orange3", "green4", "blue")
cols <- c(rep("red", 4), rep("orange3", 4), rep("green4", 4), rep("blue", 4))
plot(unlist(pctbias), unlist(noland), col = cols, cex = cexs, pch = 20, 
     ylab = "% HH without farms", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
plot(unlist(pctbias), unlist(unalloc), col = cols, cex = cexs, pch = 20, 
     ylab = "% land unallocated", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
par(xpd = NA)
xst <- seq(0.86, 0.96, 0.07 / 3)
xy <- cbind(grconvertX(xst, from = "ndc"), 
            grconvertY(rep(0.6, 5), from = "ndc"))
for(i in 2:length(xst)) {
  if(i == 2) {
    leg <- 1:4
  } else {
    leg <- rep("", 4)
  }
  legend(x = xy[i, 1], y = xy[i, 2], legend = leg, pch = 20, cex = cx[3], 
         adj = c(4.5, 0.75),  
         col = scols[i - 1], pt.cex = cexs, bty = "n")#cex = cexs,)
}
xy <- cbind(grconvertX(xst, from = "ndc"), 
            grconvertY(rep(0.58, 5), from = "ndc"))
text(x = xy[, 1], y = xy[, 2], labels = c("District", mcap), srt = 90, #pos = 2, 
     adj = c(0, 1.5), col = c("black", scols), cex = cx[1])
dev.off()

>>>>

cexs <- seq(1, 2, 1 / 3)
pdf(full_path(p_fig, "agent-bias.pdf"), height = 5, width = 3)
cx <- c(0.7, 0.8, 0.6)
# png(full_path(p_fig, "agent-bias.png"), height = 350, width = 700)
par(mfrow = c(2, 1), mar = c(0.5, 2.5, 0.5, 1), mgp = c(1, 0.05, 0), 
    tcl = -0.2, oma = c(3.5, 0, 0, 0))
scols <- c("red", "orange3", "green4", "blue")
cols <- c(rep("red", 4), rep("orange3", 4), rep("green4", 4), rep("blue", 4))
plot(unlist(pctbias), unlist(noland), col = cols, cex = cexs, pch = 20, 
     ylab = "% HH without farms", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
plot(unlist(pctbias), unlist(unalloc), col = cols, cex = cexs, pch = 20, 
     ylab = "% land unallocated", xlab = "% cropland bias", cex.lab = cx[2], 
     cex.axis = cx[1])
par(xpd = NA)

yst <- seq(0.03, 0.13, 0.07 / 3)
xy <- cbind(grconvertX(rep(0.5, 5), from = "ndc"), 
            grconvertY(yst, from = "ndc"))
for(i in 2:length(xst)) {
  if(i == 5) {
    leg <- c("District", 1:4)
  } else {
    leg <- rep("", 4)
  }
  legend(x = xy[i, 1], y = xy[i, 2], legend = rep("",4), #legend = leg, 
         pch = 20, cex = cx[3], 
         horiz = TRUE, adj = c(4, -5.75),  
         col = scols[i - 1], pt.cex = cexs, bty = "n")#cex = cexs,)
}
yst <- seq(0.005, 0.105, 0.07 / 3)
xy <- cbind(grconvertX(rep(0.55, 5), from = "ndc"), 
            grconvertY(yst, from = "ndc"))
text(x = xy[2:5, 1], y = xy[2:5, 2], labels = c(mcap),# "District"), 
     #srt = 90, #pos = 2, 
     #adj = c(-1, 1), 
     pos = 2, col = c(scols), cex = cx[1])
dev.off()
